Pareto-Optimal Multistate Protein Design using Tree Graphical Models

### 2013-01-03 docs/tex/experiments.tex
Added random features tied and untied

\subsubsection{Simulation Experiment 5 : Random feature space tied}

\subsubsection{Simulation Experiment 6 :  Random feature space untied}

>>>>

\subsubsection{Simulation Experiment 5 : Random feature space tied}
Like~\ref{sim:randprobstied} but the feature space is random
\label{sim:randfeatstied}

\subsubsection{Simulation Experiment 6 :  Random feature space untied}
Like~\ref{sim:randprobsuntied} but the feature space is random
\label{sim:randfeatsuntied}
